The \dealii Library, Version 9.1

### 2019-05-10 9.1/paper.tex
Update source of funding for myself and Timo.

W.~Bangerth was partially
supported by the National Science Foundation under award OCI-1148116
as part of the Software Infrastructure for Sustained Innovation (SI2)
program; and by the Computational Infrastructure in Geodynamics initiative
(CIG), through the National Science Foundation under Awards
No.~EAR-0949446 and EAR-1550901 and The University of California -- Davis.

@@

T.~Heister was partially supported by NSF Award DMS-1522191, by the
Computational Infrastructure in Geodynamics initiative (CIG), through the NSF
under Award EAR-0949446 and EAR-1550901 and The University of California --
Davis, and by Technical Data Analysis, Inc. through US Navy SBIR N16A-T003.

>>>>

W.~Bangerth and T.~Heister were partially
supported by the National Science Foundation under award OAC-1835673
as part of the Cyberinfrastructure for Sustained Scientific Innovation (CSSI)
program; by award DMS-1821210; and by the Computational Infrastructure
in Geodynamics initiative (CIG), through the National Science
Foundation under Awards No.~EAR-0949446 and EAR-1550901 and The
University of California -- Davis.

@@

T.~Heister was also partially supported by NSF Award DMS-1522191, and
by Technical Data Analysis, Inc. through US Navy SBIR N16A-T003.
